### 2012-09-19 hdf5/discs_2012/background.tex
Started with evaluation, writing bibliography now, included bib files

\subsection{PLFS}
PLFS is a middleware virtual file system that converts writes to a shared logical file into writes to multiple physical files. 
It is situated between the application and the parallel file system responsible for the actual data storage. 
It transforms an application's N-->1 access pattern into an N-->N access pattern, where every process participating in I/O writes data to its own , separate file. 
Thus, it interposes on application I/O and converts its I/O pattern into one that is more suitable for the underlying parallel file system.
The basic operation of PLFs is as follows. For every logical file, PLFS creates a /texit{container} structure on the underlying parallel file system. 
This container is a hierarchical directory tree consisting of multiple sub-directories. Multiple processes opening the same logical file for writing get a unique data file within the container. When the processes write to their file, a record identifying the write is appended to an index file shared between all processes. Thus, PLFS maintains sufficient metadata to recreate the shared logical file. A FUSE daemon exports this container structure as a single, logical file to the end-users, thereby keeping the PLFS operations transparent from them.

>>>>

Virtual Object Layer (VOL):
(I have simply copied this part; need to reframe it) The Virtual Object Layer (VOL) is a new abstraction layer internal to the HDF5 library (reference here). It is implemented just below the public API. The VOL intercepts all HDF5 API calls that could potentially access objects in the file and forwards those calls to an “object driver” plugin. The plugins could actually store the objects in variety of ways. A plugin could, for example, have objects be distributed remotely over different platforms, provide a raw mapping of the model to the file system, or even store the data in other file formats (like native netCDF or HDF4 format). The user still gets the same data model where access is done to a single HDF5 “container”; however the plugin object driver translates from what the user sees to how the data is actually stored.

\subsection{PLFS}
PLFS is a middleware virtual file system that converts writes to a shared logical file into writes to multiple physical files. 
It is situated between the application and the parallel file system responsible for the actual data storage. 
It transforms an application's N-->1 access pattern into an N-->N access pattern, where every process participating in I/O writes data to its own , separate file. 
Thus, it interposes on application I/O and converts its I/O pattern into one that is more suitable for the underlying parallel file system.
The basic operation of PLFs is as follows. For every logical file, PLFS creates a /texit{container} structure on the underlying parallel file system. 
This container is a hierarchical directory tree consisting of multiple sub-directories. Multiple processes opening the same logical file for writing get a unique data file within the container. When the processes write to their file, a record identifying the write is appended to an index file shared between all processes. Thus, PLFS maintains sufficient metadata to recreate the shared logical file. A FUSE daemon exports this container structure as a single, logical file to the end-users, thereby keeping the PLFS operations transparent from them. 
We added a new feature to PLFS called XAttributes (xattrs). Xattrs serve as short metadata stored as key-value pairs.
All xattrs are stored in a new directory inside the PLFS container structure. They can be used to store user-defined information about data for easy and fast retrieval, since they are not stored alongwith raw data. 
We use xattrs to store metadata about HDF5 datasets. The datatype, number of dimensions and their extent etc. are stored as xattrs.
